100 Years of Social Work Research: A Data Science Perspective

### 2015-01-05 Analysis.Rmd
Updated analysis. Everything is working.

---
title: '100 Years of Social Work Research: A Data Science Perspective'
output: pdf_document
---

@@

top.10.countries <- head(location, 10)
top.10.countries <- top.10.countries$subject.terms
top.10.countries <- levels(droplevels(top.10.countries))

@@

location <- pi.df %>%
        filter(attributes == "LO") %>%
        select(articleID = articleID, keywords = record) %>%
        filter(keywords %in% top.10.countries)

location.year <- location %>% 
         left_join(year)

@@

@@

It is easy to explore some of the different fields within the PsychInfo data frame.  For example, each record has one or more subject terms (from the article keywords).  The total number, unique number, and most frequently occuring key words can be easily computed.

```{r comment=NA, warning=FALSE, message=FALSE}

@@

subject.terms <- stringr::str_split(MD.df$record, pattern = ";")
subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
subject.terms.unique <- length(unique(subject.terms))

most.frequent <- arrange(most.frequent, desc(Freq))
most.frequent.t <- head(most.frequent, 50)

print(subject.terms.l)
print(most.frequent.t)

@@

## Methodology

```{r}
decade <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

decade$year <- cut(decade$year, breaks = 20, labels = c(1:20))

keywords <- pi.df %>%
        filter(attributes == "MD") %>%
        select(articleID = articleID, keywords = record)

keywords.decade <- lapply(keywords.data.split, terms.f)
keywords.decade <- lapply(keywords.decade, unlist)
lapply(keywords.decade, function(x) length(unique(x)))

@@

# How Many International Contributors?

This section shows a proof of concept -- that is, we can potentially extract all the countries from the author affiliation `AF` tag in the data set.  This involves using a set of regular expressions for the extraction.  Here I have hard-coded a few countries, but I can obtain a file of all countries and use that to automate the process.  We will need to look at the raw data to ensure that the author affiliations have remained in a consistent format throughtout the entirety of the study.

```{r}
df.affiliations <- pi.df %>%
                filter(attributes == "AF")

us.aff <- ifelse(grepl("US", df.affiliations$record, perl=TRUE) == TRUE, "US", 
          ifelse(grepl("Canada", df.affiliations$record, perl=TRUE ) == TRUE, "Canada", 
          ifelse(grepl("Kong", df.affiliations$record, perl=TRUE ) == TRUE, "Hong Kong", 
          ifelse(grepl("China", df.affiliations$record, perl=TRUE) == TRUE, "China", 
          ifelse(grepl("Israel", df.affiliations$record, perl=TRUE) == TRUE, "Israel", "Other" )))))

affiliations <- data.frame(cbind(df.affiliations,us.aff))

ggplot(data=df.affiliations, aes(x = factor(us.aff))) + geom_bar()
```

>>>>

---
title: '100 Years of Social Work Research: A Data Science Perspective'
output: html_document
---

@@

@@

location.temp <- pi.df %>%
        filter(attributes == "LO") %>%
        select(articleID = articleID, country = record) %>%
        mutate(country = gsub(" ", "", country))

location.year <- location.temp %>% 
         left_join(year) %>%
         group_by(country, year) %>%
         summarise(n = n()) %>%
         arrange(country, year, n)

top.locations <- location %>% 
                 select(subject.terms) %>%
                 rename(country = subject.terms) %>%
                 slice(1:5)

location.year.top <- location.year %>% filter(country %in% top.locations$country)
ggplot(location.year.top, aes(x = year, y = n, colour = country )) + geom_line()

top.locations.no.us <- location %>% 
                select(subject.terms) %>%
                rename(country = subject.terms) %>%
                slice(2:7)

location.year.top.no.us <- location.year %>% filter(country %in% top.locations.no.us$country)

ggplot(location.year.top.no.us, aes(x = year, y = n, colour = country )) + geom_line()

@@

## Countries not represented in social work research

This section is currently not functional
```{r countries_not_represented}
#Tableau.countries <- read.csv("/Users/beperron/Git/SocialWorkResearch/SupportingDocs/Tableau\ Countries.csv")
```

@@

```{r methodology, comment=NA, warning=FALSE, message=FALSE}

@@

methodology <- stringr::str_split(MD.df$record, pattern = ";")
methodology.terms <- unlist(lapply(methodology, function(x) gsub(" ", "", x)))

methodology.table <- as.data.frame(table(methodology.terms))
methodology.table <- arrange(methodology.table, desc(Freq))

@@

## Methodology over time

```{r}
year <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

methodology <- pi.df %>%
        filter(attributes == "MD") %>%
        select(articleID = articleID, method = record) %>%
        mutate(method = gsub(" ", "", method))

methodology.year <- methodology %>% 
         left_join(year) %>%
         group_by(method, year) %>%
         summarise(n = n()) %>%
         arrange(method, year, n)

methodology.year.top <- slice(methodology.table, 1:5) %>%
         rename(method = methodology.terms) %>%
         mutate(method = gsub(" ", "", method))

methodology.year.reduced <- methodology.year %>%
        filter(method %in% methodology.year.top$method)

ggplot(methodology.year.reduced, aes(x = year, y = n, colour = method)) + 
        geom_line()
```

@@
